A practical guide for selecting the spectral photon flux density distribution of light for comparing photosynthetic rates of leaves grown under different spectral light environments

### 2016-08-11 Header.Rmd
パス図をDrフォルダへ。使うかは微妙。 あとは論文中の図を微修正、本文をわずかに修正など。 3091 words

---
title: "Evaluating effects of light quality: A basis for selecting the spectral photon flux density distribution of light for measuring photosynthetic rates of leaves"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
bibliography: ~/GitHub/BeeLabR/BibTex/with.bib
csl: ECB.csl
header-includes:
  - \setmainfont{Helvetica}
  - \usepackage{zxjatype} # 日本語を使う
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォント
  - \usepackage{lscape} # 図を回転する
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command

output:
# pdf_document:
#   latex_engine: xelatex
#     toc: TRUE # table of contents
#     toc_depth: 3
#     number_sections: TRUE
#     fig_caption: TRUE
# fontsize: 12pt
# geometry: margin=1.2in
  html_document:
    toc: TRUE
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: TRUE
---

@@

evalFig <- T
if(evalFig){
  devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")
} else {
  library(knitr)
}

opts_chunk$set(cache = F, echo = FALSE, fig.width = 5, fig.height = 5,
               out.width = '500pixel', out.height = '500pixel', dpi = 100,
               message = FALSE, warning = FALSE, eval = T)
```

>>>>

---
title: "Evaluating effects of light quality: A basis for selecting the spectral photon flux density distribution of light for measuring photosynthetic rates of leaves"
author: "Keach Murakami^1\\*^, Ryo Matsuda^1^, Kazuhiro Fujiwara^1^"
csl: ECB.csl
bibliography: ~/GitHub/BeeLabR/BibTex/With.bib
header-includes:
  - \setmainfont{Times New Roman}
  # - \setmainfont{Helvetica Neue}
  - \usepackage{zxjatype} # 日本語を使うためのパッケージ
  - \setjamainfont{Hiragino Kaku Gothic Pro} # 日本語フォントの指定
  - \usepackage{lscape} # 図を回転するためのパッケージ
  - \newcommand{\blandscape}{\begin{landscape}} # 図回転用のbegin command
  - \newcommand{\elandscape}{\end{landscape}} # 図回転用のend command
  - \usepackage{setspace} # 行間の調節ためのパッケージ
  - \newcommand{\bdoublespace}{\begin{spacing}{1.5}} # 行間を広げるbegin command
  - \newcommand{\edoublespace}{\end{spacing}{1.5}} # 行間を広げるbegin command
  - \usepackage{lineno} # 行番号を追加するためのパッケージ
  - \linenumbers # 行番号を追加する

output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: TRUE
fontsize: 20pt
geometry: margin=1.2in
  # html_document:
  #   toc: TRUE
  #   depth: 3
  #   theme: sandstone
  #   self_contained: TRUE
  #   fig_caption: TRUE
  # word_document:
  #   toc: FALSE
  #   fig_caption: TRUE
---

@@

evalFig <- T
base_size <- 20
Annotate_size <- 6

source("./caption.R")
if(evalFig){
  devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")
}

knitr::opts_chunk$set(cache = F, echo = FALSE, fig.width = 7, fig.height = 7, dpi = 300,
                      message = FALSE, warning = FALSE, eval = T)
               # out.width = '500pixel', out.height = '500pixel', dpi = 100,
```

### 2016-08-11 Main.Rmd
パス図をDrフォルダへ。使うかは微妙。 あとは論文中の図を微修正、本文をわずかに修正など。 3091 words

```{r Captions}
CapEED <-
  "Fig. 1  Excitation balance between photosystems in response to wavelength of measuring light. Spectrum was calculated from absorbance spectra of PSII and PSI complexes in solvent (Hogewoning et al. 2012)."

CapETRs <-
  "Fig. 2  Conceptual diagrams of effects of excitation energy distribution between photosystems (PSII and PSI) on photosynthetic electron transport rate (ETR). Figure shows electron flow (grey lines) and energy flow (black lines) in leaves grown under PSII-light (A, B) and PSI-light (C, D) and measured using PSII-light (A, C) and PSI-light (B, D)."

CapInteract <-
  "Fig. 3  Conceptual diagram of photosynthetic electron transport rates per absorbed photons by leaves grown under PSII-light (PSII-leaves) and PSI-light (PSI-leaves) in response to the PSII/PSI-bised level of measuring light."

CapSPD <-
  'Fig. 4  Spectral photon flux density distributions of light provided by (a) fluorescent lamp (FL; FPL55EX-N<sup>1</sup>); metal halide lamp (MH; M220FCELS-W/BUD<sup>1</sup>); high-pressure sodium lamp (HPS; NH220FLS<sup>1</sup>), (b) blue (B; HBL3-3S55-LE<sup>2</sup>), red (R; SRK3-3A80-LE<sup>2</sup>), far-red (FR; L735-36AU<sup>3</sup>), and white (W; NSPW310DS<sup>4</sup>) light-emitting diodes, and (c) incident and leaf-transmitted sunlight. Distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown. Grey shading indicates far-red waveband (700--750 nm). Distribution of sunlight is from International Electrotechnical Commission Standard 60904–3 [@IEC2007]. Distribution of leaf-transmitted sunlight was calculated from that of incident sunlight and transmittance spectrum of cucumber leaf (Murakami et al. 2016).<br><sup>1</sup>IWASAKI ELECTRIC CO., LTD, Tokyo, Japan; <sup>2</sup>Tricon Co., Shimane, Japan; <sup>3</sup>Epitex Inc., Kyoto, Japan; <sup>4</sup>Nichia Chemical Industries Ltd., Tokushima, Japan.'
```

@@

InteractionView <-
  InteractionDat %>%
  ggplot(aes(X, ETR, linetype = Trtm, fill = Trtm, group = Trtm)) +
  theme_bw2() +
  theme(axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major = element_blank()) +
  geom_vline(aes(xintercept = x_breaks[1]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[2]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[3]), linetype = 3, size = .75, col = "grey") +
  geom_line() +
  geom_point(data = InteractionPoint, col = "black", size = 3, shape = 21) +
  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1) +
  geom_text(data = InteractionText, aes(label = labels), vjust = 1) +
  scale_fill_manual(values = c("white", "black")) +
  scale_linetype_manual(values = c(2, 1)) +
  scale_x_continuous(breaks = c(0.07, 0.92), limits = c(0.05, 0.95), labels = c("PSI-biased", "PSII-biased")) +
  xlab("PSII/PSI-biased level of measuring light") +
  ylab("Relative electron transport rate") +
  gg_y(c(0, 2))
```

EEDs <-
  EED_dat %>%
    mutate(All2_for = c(tail(EED_dat$AlltoPSII, -1), 0),
           All2_back = c(0, head(EED_dat$AlltoPSII, -1)),
           AlltoPSII = (AlltoPSII + All2_for + All2_back) / 3) %>% # get moving average
    filter(wavelength > 400)  %>%
    replace_na(list(AlltoPSII = 0)) %>%
    ggplot(aes(x = wavelength, y = AlltoPSII)) +
    theme_bw2() +
    theme(panel.grid.major = element_blank()) +
    geom_hline(yintercept = 0.5, col = "grey50", linetype = 3) +
    gg_x(c(380, 770)) +
    # geom_ribbon(aes(ymin = AlltoPSII_max, ymax = AlltoPSII_min), col = "grey50") +
    geom_line() +
    scale_y_continuous(labels = c("0    ", "0.25", "0.50", "0.75", "1.00"),
                       breaks = c(0, 0.25, 0.5, 0.75, 1),
                       limits = c(0, 1.0),
                       expand = c(0, 0)) +
    xlab("Wavelength [nm]") + ylab("Fraction of the excitation energy distributed to PSII")
```

@@

SPD_labels <-
  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 700),
             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf transmitted sunlight"),
             panel = rep(panel_names,  c(3, 4, 2)))

@@

SPDs <-
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[3]) %>%
  bind_rows(., OceanSPDs, LEDs) %>%
  filter(between(wavelength, 380, 820)) %>%
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
  theme_bw2() +
  theme(strip.background = element_blank(),
        strip.text = element_blank(),
        panel.grid.major = element_blank()) +
  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
  geom_line() +
  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
  geom_text(data = SPD_panel, col = "black", aes(label = panel)) +
  scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey25", "black", "black")) +
  facet_grid(panel ~ .) +
  gg_xy(c(380, 820, 0, 4.5)) +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

```{r, eval = evalFig, html.cap = CapEED}
EEDs
```

@@

```{r, eval = evalFig, html.cap = CapInteract}
InteractionView
```

```{r, eval = evalFig, html.cap = CapSPD}
SPDs
```

>>>>

EEDs <-
  EED_dat %>%
    mutate(All2_for = c(tail(EED_dat$AlltoPSII, -1), 0),
           All2_back = c(0, head(EED_dat$AlltoPSII, -1)),
           AlltoPSII = (AlltoPSII + All2_for + All2_back) / 3) %>% # get moving average
    filter(wavelength > 400)  %>%
    replace_na(list(AlltoPSII = 0)) %>%
    ggplot(aes(x = wavelength, y = AlltoPSII)) +
    theme_thesis(base_family = "serif", base_size = base_size) +
    geom_hline(yintercept = 0.5, col = "grey50", linetype = 3) +
    gg_x(c(380, 770)) +
    # geom_ribbon(aes(ymin = AlltoPSII_max, ymax = AlltoPSII_min), col = "grey50") +
    geom_line() +
    scale_y_continuous(labels = c("0    ", "0.25", "0.50", "0.75", "1.00"),
                       breaks = c(0, 0.25, 0.5, 0.75, 1),
                       limits = c(-.005, 1.005),
                       expand = c(0, 0)) +
    xlab("Wavelength [nm]") + ylab("Fraction of the excitation energy distributed to PSII")
```

@@

InteractionView <-
  InteractionDat %>%
  ggplot(aes(X, ETR, linetype = Trtm, fill = Trtm, group = Trtm)) +
  theme_thesis(base_family = "serif", base_size = base_size) +
  geom_vline(aes(xintercept = x_breaks[1]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[2]), linetype = 3, size = .75, col = "grey") +
  geom_vline(aes(xintercept = x_breaks[3]), linetype = 3, size = .75, col = "grey") +
  geom_line() +
  geom_point(data = InteractionPoint, col = "black", size = 3, shape = 21) +
  geom_text(data = InteractionLabel, aes(x = X, y = ETR, label = Trtm), vjust = -1, family = "serif", size = Annotate_size) +
  geom_text(data = InteractionText, aes(label = labels), vjust = 1, family = "serif", size = Annotate_size) +
  scale_fill_manual(values = c("white", "black")) +
  scale_linetype_manual(values = c(2, 1)) +
  scale_x_continuous(breaks = c(0.07, 0.92),
                     limits = c(0.05, 0.95),
                     labels = c("PSI-biased", "PSII-biased")) +
  scale_y_continuous(breaks = NULL,
                     limits = c(-0.05, 2.05)) +
  xlab("PSII/PSI-biased level of measuring light") +
  ylab("Relative electron transport rate")

@@

SPD_labels <-
  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 700),
             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf-transmitted sunlight"),
             panel = rep(panel_names,  c(3, 4, 2)))

@@

SPDs <-
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[3]) %>%
  bind_rows(., OceanSPDs, LEDs) %>%
  filter(between(wavelength, 380, 820)) %>%
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
  theme_thesis(base_family = "serif", base_size = base_size) +
  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
  geom_line() +
  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label), family = "serif", size = Annotate_size) +
  geom_text(data = SPD_panel, col = "black", aes(label = panel), family = "serif", size = Annotate_size * .8) +
  scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey25", "black", "black")) +
  facet_grid(panel ~ .) +
  gg_xy(c(380, 820, -.01, 4.5)) +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))
```

```{r, eval = evalFig, html.cap = CapEED}
EEDs
# pdf("./Figs/EEDs.pdf", family = "Times", width = 3.15, height = 2.5)
#   EEDs + theme_thesis(base_size = 5)
# dev.off()
```

@@

```{r, eval = evalFig, html.cap = CapInteract}
InteractionView
# pdf("./Figs/Interactions.pdf", family = "Times", width = 3.15, height = 2.5)
#   InteractionView + theme_thesis(base_size = 5)
# dev.off()
```

```{r, eval = evalFig, html.cap = CapSPD}
SPDs
# pdf("./Figs/SPDs.pdf", family = "Times", width = 3.15, height = 4)
#   InteractionView + theme_thesis(base_size = 5)
# dev.off()
```
